Transfer report

### 2018-06-19 Report/iNav-data.Rmd
Adds 3-4 bloÃcks

conference_walk_all <- walk_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
conference_sop_all <- sop_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
load("../multi_smoothed.data")
```

```{r setup, include=F}
#green, violet, blue, yellow, pink, dark blue
estimote_pal <- c('#b6d6c1', '#54003d','#93d5f6','#d5d215','#f3aacb','#2d2556')
theme_set(theme_minimal())
```

@@

## Independent block improvement comparisons between conditions

@@

### Block 3-4 improvement
VE-real and real-real
```{r, echo=F}
t.test(df_wide$diff43[df_wide$learning.condition=="Desktop"], df_wide$diff43[df_wide$learning.condition=="Real"])
```

>>>>

conference_walk_all <- walk_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
conference_sop_all <- sop_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
load("../multi_smoothed.data")

#green, violet, blue, yellow, pink, dark blue
estimote_pal <- c('#b6d6c1', '#54003d','#93d5f6','#d5d215','#f3aacb','#2d2556')
theme_set(theme_minimal())
```

@@

## Independent block improvement comparisons between conditions for distance

@@

### Block 3-4 improvement
Desktop to real
```{r, echo=F}
t.test(df_wide$diff43[df_wide$learning.condition=="Desktop"], df_wide$diff43[df_wide$learning.condition=="Real"])
```

## Independent block improvement comparisons between conditions for number of errors

```{r, echo=F}
df_wide <- dcast(condition_all_sums, learning.condition + id ~ exp_block_id, value.var = "sum.errors")
colnames(df_wide) <- c("learning.condition","id", "block1","block2","block3","block4","block5","block6")
df_wide$diff41 <- (df_wide$block4-df_wide$block1)/(df_wide$block1+df_wide$block3)
df_wide$diff43<- (df_wide$block4-df_wide$block3)/(df_wide$block4+df_wide$block3)
```

### Block 3-4 improvement
Desktop to real
```{r, echo=F}
t.test(df_wide$diff43[df_wide$learning.condition=="Desktop"], df_wide$diff43[df_wide$learning.condition=="Real"])
```
